Text embedding models yield high-resolution insights into conceptual knowledge from short multiple-choice quizzes

### 2023-02-22 paper/main.tex
fixed supplementary figure names and references in main text

% supplemental tables
\newcommand{\questions}{S1}
\newcommand{\topics}{S2}

% supplemental figures
\newcommand{\topicWeights}{S1} 
\newcommand{\individualKnowledgeMapsA}{S2}
\newcommand{\individualKnowledgeMapsB}{S3}
\newcommand{\individualKnowledgeMapsC}{S4}
\newcommand{\individualLearningMapsA}{S5}
\newcommand{\individualLearningMapsB}{S6}

@@

At its core, our main modeling approach is based around a simple assumption
that we sought to test empirically: all else being equal, knowledge about a
given concept is predictive of knowledge about similar or related concepts.
From a geometric perspective, this assumption implies that knowledge is
fundamentally ``smooth.'' In other words, as one moves through a space
representing an individual's knowledge (where similar concepts occupy nearby
coordinates), their ``level of knowledge'' should change relatively gradually
throughout that space. To begin to test this smoothness assumption, we sought
to track participants' knowledge and how it changed over time in response to
training. Two overarching goals guide our approach. First, we want to gain
detailed insights into what learners know, at different points in their
training. For example, rather than simply reporting on the proportions of
questions participants answer correctly (i.e., their overall performance), we
seek estimates of their knowledge about a variety of specific concepts.
Second, we want our approach to be potentially scalable to large numbers of
concepts, courses, and students. This requires that the conceptual content of
interest be discovered \textit{automatically}, rather than relying on
manually produced ratings or labels.

@@

We asked participants in our study to complete brief multiple-choice quizzes
before, between, and after watching two lecture videos from the Khan
Academy~\citep{Khan04} platform (Fig.~\ref{fig:experiment}). The first lecture
video, entitled \textit{Four Fundamental Forces}, discussed the four
fundamental forces in physics: gravity, strong and weak interactions, and
electromagnetism. The second, entitled \textit{Birth of Stars}, provided an
overview of our current understanding of how stars form. We selected these
particular lectures to satisfy three general criteria. First, we wanted both
lectures to be accessible to a broad audience (i.e., with minimal prerequisite
knowledge) so as to limit the impact of prior training on our participants'
abilities to learn from the lectures. To this end, we selected two introductory
videos that were intended to be viewed at the start of students' training in
their respective content areas. Second, we wanted both lectures to have some
related content, so that we could test our approach's ability to distinguish
similar conceptual content. To this end, we chose two videos from the same (per
instructor annotations) Khan Academy course domain, ``Cosmology and
Astronomy.'' Third, we sought to minimize dependencies and specific overlap
between the videos. For example, we did not want participants' abilities to
understand one video to (directly) influence their abilities to understand the
other. To satisfy this last criterion, we chose videos from two different
lecture series (Lectures~1 and 2 were from the ``Scale of the Universe'' and
``Stars, Black Holes, and Galaxies'' series, respectively).

We also wrote a set of multiple-choice quiz questions that we hoped would
enable us to evaluate participants' knowledge about each individual lecture,
along with related knowledge about physics not specifically presented in either
video (see Tab.~\questions~for the full list of questions in our stimulus
pool). Participants answered questions randomly drawn from each content area
(Lecture~1, Lecture~2, and general physics knowledge) on each of the three
quizzes. Quiz~1 was intended to assess participants' ``baseline'' knowledge
before training, Quiz~2 assessed knowledge after watching the \textit{Four
Fundamental Forces} video (i.e., Lecture~1), and Quiz~3 assessed knowledge
after watching the \textit{Birth of Stars} video (i.e., Lecture~2).

@@

\caption{\textbf{Modeling course content.} \textbf{A. Building a document pool
from sliding windows of text.} We decompose each lecture's transcript into a
series of overlapping sliding windows. The full set of transcript snippets (across
all windows) may be treated as a set of ``documents'' for training a text
embedding model. \textbf{B. Constructing lecture content
\textit{trajectories}.} After training our model on the sliding windows from
both lectures, we transform each lecture into a ``trajectory'' through text
embedding space by joining the embedding coordinates of successive sliding
windows parsed from its transcript. \textbf{C. Embedding multiple lectures and
questions in a shared space.} We apply the same model (trained on the two
lectures' windows) to both lectures, along with the text of each question in
our pool (Tab.~\questions), to project them into a shared text embedding space.
This results in one trajectory per lecture and one coordinate for each
question. Here, we have projected the 15-dimensional embeddings onto their first
3 principal components for visualization.}

@@

We hypothesized that a topic model trained on transcripts of the two lectures
should also capture the conceptual knowledge probed by each quiz question. If
indeed the topic model could capture information about the deeper conceptual
content of the lectures (i.e., beyond surface-level details such as particular
word choices), then we should be able to recover a correspondence between each
lecture and questions \textit{about} each lecture. Importantly, such a
correspondence could not solely arise from superficial text matching between
lecture transcripts and questions, since the lectures and questions used
different words. Simply comparing the average topic weights from each lecture
and question set (averaging across time and questions, respectively) reveals a
striking correspondence (Fig.~\topicWeights). Specifically, the average topic
weights from Lecture~1 are strongly correlated with the average topic weights
from Lecture~1 questions ($r(13) = 0.809,~p < 0.001$, 95\% confidence interval
(CI)~$= [0.633,~0.962]$), and the average topic weights from Lecture~2 are
strongly correlated with the average topic weights from Lecture~2 questions
($r(13) = 0.728,~p = 0.002$, 95\% CI~$= [0.456,~0.920]$). At the same time, the
average topic weights from the two lectures are \textit{negatively} correlated with 
their non-matching question sets (Lecture~1 video vs.~Lecture~2 questions: $r(13) = 
-0.547,~p = 0.035$, 95\% CI~$= [-0.812, ~-0.231]$; Lecture~2 video vs.~Lecture~1 questions: $r(13) 
= -0.612,~p = 0.015$, 95\% CI~$= [-0.874,~-0.281]$), indicating that the topic model
also exhibits some degree of specificity. The full set of pairwise comparisons
between average topic weights for the lectures and question sets is reported in
Figure~\topicWeights.

@@

\caption{\textbf{Lecture and question topic overlap.} \textbf{A. Topic weight
variability}. The bar plots display the variance of each topic's weight across
lecture timepoints (top row) and questions (bottom row); colors denote topics.
The top-weighted words from the most ``expressive'' (i.e., variable across
observations) topic from each lecture are displayed in the upper right (orange:
topic 2; yellow-green: topic 4). The top-weighted words from the full set of
topics may be found in Table~\topics. \textbf{B. Relationships between topic
weight variability.} Pairwise correlations between the distributions of topic
weight variance for each lecture and question set. Each row and column
corresponds to a bar plot in Panel A.}

@@

Another, more sensitive, way of summarizing the conceptual content of the
lectures and questions is to look at \textit{variability} in how topics are
weighted over time and across different questions (Fig.~\ref{fig:topics}).
Intuitively, the variability in the expression of a given topic relates to how
much ``information''~\citep{Fish22} the lecture (or question set) reflects about
that topic. For example, suppose a given topic is weighted on heavily
throughout a lecture. That topic might be characteristic of some aspect or
property of the lecture \textit{overall} (conceptual or otherwise), but unless
the topic's weights changed in meaningful ways over time, the topic would be a
poor indicator of any \textit{specific} conceptual content in the lecture. We
therefore also compared the variances in topic weights (across time or
questions) between the lectures and questions. The variability in topic
expression (over time and across questions) was similar for the Lecture~1 video
and questions ($r(13) = 0.824,~p<0.001$, 95\% CI~$= [0.696,~0.973]$) and the Lecture~2
video and questions ($r(13) = 0.801,~p<0.001$, 95\% CI~$= [0.539,~0.958]$). 
However, as reported in Figure~\ref{fig:topics}B, the variability in
topic expressions across \textit{different} videos and lecture-specific
questions (i.e., Lecture~1 video vs.~Lecture~2 questions; Lecture~2 video
vs.~Lecture~1 questions) were negatively correlated, and neither
video's topic variability was reliably correlated with the topic variability
across general physics knowledge questions. Taken together, the analyses
reported in Figures~\ref{fig:topics} and~\topicWeights~indicate that a topic
model fit to the videos' transcripts can also reveal correspondences (at a
coarse scale) between the lectures and questions.

@@

    \caption{\textbf{Mapping out the geometry of knowledge and learning.}
    \textbf{A. Average ``knowledge maps'' estimated using each quiz.} Each map
    displays a 2D projection of the estimated knowledge about the content
    reflected by \textit{all} regions of topic space (see
    \nameref{subsec:knowledge-maps}). The topic trajectories of each
    lecture are indicated by dotted lines, and the coordinates of each question are indicated by
    dots. Each map reflects an average across all participants. For
    individual participants' maps, see
    Figures~\individualKnowledgeMapsA,~\individualKnowledgeMapsB,
    and~\individualKnowledgeMapsC. \textbf{B. Average ``learning maps''
    estimated between each successive pair of quizzes.} The learning maps follow
    the same general format as the knowledge maps in Panel A, but here the shading at each
    coordinate indicates the \textit{difference} between
    the corresponding coordinates in the indicated \textit{pair} of knowledge
    maps---i.e., how much the estimated knowledge ``changed'' between the two
    quizzes. Each map reflects an average across all participants. For
    individual participants' maps, see
    Figures~\individualLearningMapsA~and~\individualLearningMapsB. \textbf{C.
    Word clouds for sampled points in topic space.} Each word cloud displays
    the relative weights of each word (via their relative sizes) reflected by the blend of topics
    represented at the locations of the stars on the maps. The words' colors
    indicate how much each word is weighted, on average, across all timepoints'
    topic vectors in the \textit{Four Fundamental Forces} (blue) and
    \textit{Birth of Stars} (green) videos, respectively.}

@@

We hand-selected two course videos from the Khan Academy platform: \textit{Four
Fundamental Forces} (an introduction to gravity, electromagnetism, the weak
nuclear force, and the strong nuclear force; duration: 10 minutes and 29
seconds) and \textit{Birth of Stars} (an introduction to how stars are formed;
duration: 7 minutes and 57 seconds). We then hand-created 39 multiple-choice
questions: 15 about the conceptual content of \textit{Four Fundamental Forces} (i.e., Lecture~1),
15 about the conceptual content of \textit{Birth of Stars} (i.e., Lecture~2), and 9
questions that tested for general conceptual knowledge about basic physics
(covering material that was not presented in either video). The full set of
questions and answer choices may be found in Table~\questions.

@@

We fetched these automated transcripts using the
\texttt{youtube-transcript-api} Python package~\citep{Depo19}. The transcripts
consisted of one timestamped line of text for every few seconds (mean: 2.34~s;
standard deviation: 0.83~s) of spoken content in the video (i.e., corresponding
to each individual caption that would appear on-screen if viewing the lecture
via YouTube, and when those lines would appear). We defined a sliding window
length of (up to) $w = 30$ transcript lines, and assigned each window a
timestamp corresponding to the midpoint between its first and last lines'
timestamps. These sliding windows ramped up and down in length at the very
beginning and end of the transcript, respectively. In other words, the first
sliding window covered only the first line from the transcript; the second
sliding window covered the first two lines; and so on. This insured that each
line of the transcript appeared in the same number ($w$) of sliding windows.
After performing various standard text preprocessing (e.g., normalizing case,
lemmatizing, removing punctuation and stop-words), we treated the text from
each sliding window as a single ``document,'' and combined these documents
across the two videos' windows to create a single training corpus for the topic
model. The top words from each of the 15 discovered topics may be found in
Table~\topics.

@@

We transformed each sliding window's text into a topic vector, and then used
linear interpolation (independently for each topic dimension) to resample the
resulting timeseries to one vector per second. We also used the fitted model to
obtain topic vectors for each question in our pool (Tab.~\questions). Taken
together, we obtained a \textit{trajectory} for each video, describing its path
through topic space, and a single coordinate for each question
(Fig.~\ref{fig:sliding-windows}C). Embedding both videos and all of the
questions using a common model enables us to compare the content from different
moments of videos, compare the content across videos, and estimate potential
associations between specific questions and specific moments of video.

@@

An important feature of our approach is that, given a trained text embedding
model and participants' quiz performance on each question, we can estimate
their knowledge about \textit{any} content expressible by the embedding
model---not solely the content explicitly probed by the quiz questions or even
appearing in the lectures. To visualize these estimates
(Figs.~\ref{fig:knowledge-maps},~\individualKnowledgeMapsA,~\individualKnowledgeMapsB,~\individualKnowledgeMapsC,~\individualLearningMapsA,
and~\individualLearningMapsB), we used Uniform Manifold Approximation and
Projection (UMAP; \citealp{McInEtal18a}) to construct a 2D projection of the
text embedding space. Sampling the original 100-dimensional space at high
resolution to obtain an adequate set of topic vectors spanning the embedding
space would be computationally intractable. However, sampling a 2D grid is
trivial.

>>>>

% supplemental tables
\newcommand{\questions}{1}
\newcommand{\topics}{2}

% supplemental figures
\newcommand{\topicWeights}{1} 
\newcommand{\individualKnowledgeMapsA}{2}
\newcommand{\individualKnowledgeMapsB}{3}
\newcommand{\individualKnowledgeMapsC}{4}
\newcommand{\individualLearningMapsA}{5}
\newcommand{\individualLearningMapsB}{6}

@@

At its core, our main modeling approach is based around a simple assumption
that we sought to test empirically: all else being equal, knowledge about a
given concept is predictive of knowledge about similar or related concepts.
From a geometric perspective, this assumption implies that knowledge is
fundamentally ``smooth.'' In other words, as one moves through a space
representing an individual's knowledge (where similar concepts occupy nearby
coordinates), their ``level of knowledge'' should change relatively gradually. 
To begin to test this smoothness assumption, we sought
to track participants' knowledge and how it changed over time in response to
training. Two overarching goals guide our approach. First, we want to gain
detailed insights into what learners know at different points in their
training. For example, rather than simply reporting on the proportions of
questions participants answer correctly (i.e., their overall performance), we
seek estimates of their knowledge about a variety of specific concepts.
Second, we want our approach to be potentially scalable to large numbers of
diverse concepts, courses, and students. This requires that the conceptual content of
interest be discovered \textit{automatically}, rather than relying on
manually produced ratings or labels.

@@

We asked participants in our study to complete brief multiple-choice quizzes
before, between, and after watching two lecture videos from the Khan
Academy~\citep{Khan04} platform (Fig.~\ref{fig:experiment}). The first lecture
video, entitled \textit{Four Fundamental Forces}, discussed the four
fundamental forces in physics: gravity, strong and weak interactions, and
electromagnetism. The second, entitled \textit{Birth of Stars}, provided an
overview of our current understanding of how stars form. We selected these
particular lectures to satisfy three general criteria. First, we wanted both
lectures to be accessible to a broad audience (i.e., with minimal prerequisite
knowledge) so as to limit the impact of prior training on our participants'
abilities to learn from the lectures. To this end, we selected two introductory
videos that were intended to be viewed at the start of students' training in
their respective content areas. Second, we wanted the two lectures to have some
related content, so that we could test our approach's ability to distinguish
similar conceptual content. To this end, we chose two videos from the same (per
instructor annotations) Khan Academy course domain, ``Cosmology and
Astronomy.'' Third, we sought to minimize dependencies and specific overlap
between the videos. For example, we did not want participants' abilities to
understand one video to (directly) influence their abilities to understand the
other. To satisfy this last criterion, we chose videos from two different
lecture series (Lectures~1 and 2 were from the ``Scale of the Universe'' and
``Stars, Black Holes, and Galaxies'' series, respectively).

We also wrote a set of multiple-choice quiz questions that we hoped would
enable us to evaluate participants' knowledge about each individual lecture,
along with related knowledge about physics not specifically presented in either
video (see Supplementary Tab.~\questions~for the full list of questions in our stimulus
pool). Participants answered questions randomly drawn from each content area
(Lecture~1, Lecture~2, and general physics knowledge) on each of the three
quizzes. Quiz~1 was intended to assess participants' ``baseline'' knowledge
before training, Quiz~2 assessed knowledge after watching the \textit{Four
Fundamental Forces} video (i.e., Lecture~1), and Quiz~3 assessed knowledge
after watching the \textit{Birth of Stars} video (i.e., Lecture~2).

@@

\caption{\textbf{Modeling course content.} \textbf{A. Building a document pool
from sliding windows of text.} We decompose each lecture's transcript into a
series of overlapping sliding windows. The full set of transcript snippets (across
all windows) may be treated as a set of ``documents'' for training a text
embedding model. \textbf{B. Constructing lecture content
\textit{trajectories}.} After training our model on the sliding windows from
both lectures, we transform each lecture into a ``trajectory'' through text
embedding space by joining the embedding coordinates of successive sliding
windows parsed from its transcript. \textbf{C. Embedding multiple lectures and
questions in a shared space.} We apply the same model (trained on the two
lectures' windows) to both lectures, along with the text of each question in
our pool (Supplementary Tab.~\questions), to project them into a shared text embedding space.
This results in one trajectory per lecture and one coordinate for each
question. Here, we have projected the 15-dimensional embeddings onto their first
3 principal components for visualization.}

@@

We hypothesized that a topic model trained on transcripts of the two lectures
should also capture the conceptual knowledge probed by each quiz question. If
indeed the topic model could capture information about the deeper conceptual
content of the lectures (i.e., beyond surface-level details such as particular
word choices), then we should be able to recover a correspondence between each
lecture and questions \textit{about} each lecture. Importantly, such a
correspondence could not solely arise from superficial text matching between
lecture transcripts and questions, since the lectures and questions used
different words. Simply comparing the average topic weights from each lecture
and question set (averaging across time and questions, respectively) reveals a
striking correspondence (Supplementary Fig.~\topicWeights). Specifically, the average topic
weights from Lecture~1 are strongly correlated with the average topic weights
from Lecture~1 questions ($r(13) = 0.809,~p < 0.001$, 95\% confidence interval
(CI)~$= [0.633,~0.962]$), and the average topic weights from Lecture~2 are
strongly correlated with the average topic weights from Lecture~2 questions
($r(13) = 0.728,~p = 0.002$, 95\% CI~$= [0.456,~0.920]$). At the same time, the
average topic weights from the two lectures are \textit{negatively} correlated with 
their non-matching question sets (Lecture~1 video vs.~Lecture~2 questions: $r(13) = 
-0.547,~p = 0.035$, 95\% CI~$= [-0.812, ~-0.231]$; Lecture~2 video vs.~Lecture~1 questions: $r(13) 
= -0.612,~p = 0.015$, 95\% CI~$= [-0.874,~-0.281]$), indicating that the topic model
also exhibits some degree of specificity. The full set of pairwise comparisons
between average topic weights for the lectures and question sets is reported in
Supplementary Figure~\topicWeights.

@@

\caption{\textbf{Lecture and question topic overlap.} \textbf{A. Topic weight
variability}. The bar plots display the variance of each topic's weight across
lecture timepoints (top row) and questions (bottom row); colors denote topics.
The top-weighted words from the most ``expressive'' (i.e., variable across
observations) topic from each lecture are displayed in the upper right (orange:
topic 2; yellow-green: topic 4). The top-weighted words from the full set of
topics may be found in Supplementary Table~\topics. \textbf{B. Relationships between topic
weight variability.} Pairwise correlations between the distributions of topic
weight variance for each lecture and question set. Each row and column
corresponds to a bar plot in Panel A.}

@@

Another, more sensitive, way of summarizing the conceptual content of the
lectures and questions is to look at \textit{variability} in how topics are
weighted over time and across different questions (Fig.~\ref{fig:topics}).
Intuitively, the variability in the expression of a given topic relates to how
much ``information''~\citep{Fish22} the lecture (or question set) reflects about
that topic. For example, suppose a given topic is weighted on heavily
throughout a lecture. That topic might be characteristic of some aspect or
property of the lecture \textit{overall} (conceptual or otherwise), but unless
the topic's weights changed in meaningful ways over time, the topic would be a
poor indicator of any \textit{specific} conceptual content in the lecture. We
therefore also compared the variances in topic weights (across time or
questions) between the lectures and questions. The variability in topic
expression (over time and across questions) was similar for the Lecture~1 video
and questions ($r(13) = 0.824,~p<0.001$, 95\% CI~$= [0.696,~0.973]$) and the Lecture~2
video and questions ($r(13) = 0.801,~p<0.001$, 95\% CI~$= [0.539,~0.958]$). 
However, as reported in Figure~\ref{fig:topics}B, the variability in
topic expressions across \textit{different} videos and lecture-specific
questions (i.e., Lecture~1 video vs.~Lecture~2 questions; Lecture~2 video
vs.~Lecture~1 questions) were negatively correlated, and neither
video's topic variability was reliably correlated with the topic variability
across general physics knowledge questions. Taken together, the analyses
reported in Figure~\ref{fig:topics} and Supplementary Figure~\topicWeights~indicate that a topic
model fit to the videos' transcripts can also reveal correspondences (at a
coarse scale) between the lectures and questions.

@@

    \caption{\textbf{Mapping out the geometry of knowledge and learning.}
    \textbf{A. Average ``knowledge maps'' estimated using each quiz.} Each map
    displays a 2D projection of the estimated knowledge about the content
    reflected by \textit{all} regions of topic space (see
    \nameref{subsec:knowledge-maps}). The topic trajectories of each
    lecture are indicated by dotted lines, and the coordinates of each question are indicated by
    dots. Each map reflects an average across all participants. For
    individual participants' maps, see
    Supplementary Figures~\individualKnowledgeMapsA,~\individualKnowledgeMapsB,
    and~\individualKnowledgeMapsC. \textbf{B. Average ``learning maps''
    estimated between each successive pair of quizzes.} The learning maps follow
    the same general format as the knowledge maps in Panel A, but here the shading at each
    coordinate indicates the \textit{difference} between
    the corresponding coordinates in the indicated \textit{pair} of knowledge
    maps---i.e., how much the estimated knowledge ``changed'' between the two
    quizzes. Each map reflects an average across all participants. For
    individual participants' maps, see Supplementary
    Figures~\individualLearningMapsA~and~\individualLearningMapsB. \textbf{C.
    Word clouds for sampled points in topic space.} Each word cloud displays
    the relative weights of each word (via their relative sizes) reflected by the blend of topics
    represented at the locations of the stars on the maps. The words' colors
    indicate how much each word is weighted, on average, across all timepoints'
    topic vectors in the \textit{Four Fundamental Forces} (blue) and
    \textit{Birth of Stars} (green) videos, respectively.}

@@

We hand-selected two course videos from the Khan Academy platform: \textit{Four
Fundamental Forces} (an introduction to gravity, electromagnetism, the weak
nuclear force, and the strong nuclear force; duration: 10 minutes and 29
seconds) and \textit{Birth of Stars} (an introduction to how stars are formed;
duration: 7 minutes and 57 seconds). We then hand-created 39 multiple-choice
questions: 15 about the conceptual content of \textit{Four Fundamental Forces} (i.e., Lecture~1),
15 about the conceptual content of \textit{Birth of Stars} (i.e., Lecture~2), and 9
questions that tested for general conceptual knowledge about basic physics
(covering material that was not presented in either video). The full set of
questions and answer choices may be found in Supplementary Table~\questions.

@@

We fetched these automated transcripts using the
\texttt{youtube-transcript-api} Python package~\citep{Depo19}. The transcripts
consisted of one timestamped line of text for every few seconds (mean: 2.34~s;
standard deviation: 0.83~s) of spoken content in the video (i.e., corresponding
to each individual caption that would appear on-screen if viewing the lecture
via YouTube, and when those lines would appear). We defined a sliding window
length of (up to) $w = 30$ transcript lines, and assigned each window a
timestamp corresponding to the midpoint between its first and last lines'
timestamps. These sliding windows ramped up and down in length at the very
beginning and end of the transcript, respectively. In other words, the first
sliding window covered only the first line from the transcript; the second
sliding window covered the first two lines; and so on. This insured that each
line of the transcript appeared in the same number ($w$) of sliding windows.
After performing various standard text preprocessing (e.g., normalizing case,
lemmatizing, removing punctuation and stop-words), we treated the text from
each sliding window as a single ``document,'' and combined these documents
across the two videos' windows to create a single training corpus for the topic
model. The top words from each of the 15 discovered topics may be found in
Supplementary Table~\topics.

@@

We transformed each sliding window's text into a topic vector, and then used
linear interpolation (independently for each topic dimension) to resample the
resulting timeseries to one vector per second. We also used the fitted model to
obtain topic vectors for each question in our pool (Supplementary Tab.~\questions). Taken
together, we obtained a \textit{trajectory} for each video, describing its path
through topic space, and a single coordinate for each question
(Fig.~\ref{fig:sliding-windows}C). Embedding both videos and all of the
questions using a common model enables us to compare the content from different
moments of videos, compare the content across videos, and estimate potential
associations between specific questions and specific moments of video.

@@

An important feature of our approach is that, given a trained text embedding
model and participants' quiz performance on each question, we can estimate
their knowledge about \textit{any} content expressible by the embedding
model---not solely the content explicitly probed by the quiz questions or even
appearing in the lectures. To visualize these estimates
(Fig.~\ref{fig:knowledge-maps}, Supplementary Figs.~\individualKnowledgeMapsA,~\individualKnowledgeMapsB,~\individualKnowledgeMapsC,~\individualLearningMapsA,
and~\individualLearningMapsB), we used Uniform Manifold Approximation and
Projection (UMAP; \citealp{McInEtal18a}) to construct a 2D projection of the
text embedding space. Sampling the original 100-dimensional space at high
resolution to obtain an adequate set of topic vectors spanning the embedding
space would be computationally intractable. However, sampling a 2D grid is
trivial.
